---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ERFE – Expectile Regression for Fixed Effects

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/erfe)](https://CRAN.R-project.org/package=erfe)
[![Codecov test coverage](https://codecov.io/gh/amadoudiogobarry/erfe/branch/master/graph/badge.svg)](https://app.codecov.io/gh/amadoudiogobarry/erfe?branch=master)
<!-- badges: end -->

## What is ERFE
**ERFE** is a expectile-based method for panel data. The **ERFE** model applies the within transformation strategy to solve the incidental parameter problem and estimates the regressor effects on the expectiles of the response distribution. The **ERFE** model captures the data heteroscedasticity and eliminates any bias resulting from the correlation between the regressors and the omitted factors. When $\tau=0.5$ the ERFE model estimator corresponds to the fixed-effects within estimator.

## How to use the ERFE package
The main function of the package is the <code> erfe </code> function and consists of four arguments. The <code> predictors </code> argument which corresponds to the design matrix or the matrix of regressors. Note that, the design matrix should contain time varying regressors only, because the **ERFE** model do not make inference for time-invariant regressors. The <code> response </code> argument is the continuous response variable, and the <code> asymp </code> argument corresponds to the vector of asymmetric points with default values: $(0.25, \ 0.5, \ 0.75).$ The <code> id </code> argument corresponds to the subject ids and should be ordered according to the time or years variable.  

## Installation

You can install the development version of **ERFE** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("amadoudiogobarry/erfe")
```

## Example

This is a basic example which shows you how to use the main function of the package:

```{r example1}
library(erfe)
data(sim_panel_data) # Toy dataset
head(sim_panel_data) 

asymp <- c(0.25,0.5,0.75) # sequence of asymmetric points
predictors <- cbind(sim_panel_data$pred1, sim_panel_data$pred2) # design matrix
response <- sim_panel_data$resp # response variable
id <- sim_panel_data$id # ordered subject ids variable
outlist <- erfe(predictors, response, asymp=c(0.25,0.5,0.75), id)
```

For each asymmetric point we have a list of results including the asymmetric point itself, the estimator and the estimator of its covariance matrix, and the residuals of the model. For example, the results of the **ERFE** model for $\tau=0.75$ can be retrieved like this: 

```{r example2}
outlist75 <- outlist[[3]]
# coef estimate
outlist75$coefEst
# covariance estimate
outlist75$covMat

```



<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>. -->




